Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2017-07-25 paper/paper.tex
Updated plottery

@@

@@

    of \cref{figure:non-induced}. The fifth row plots constrainedness using

@@

    location of the phase transition, and the dotted lines are $t_d=0.5$ and the $p_d=t_d$ diagonal.}\label{figure:induced}

>>>>

\usepackage{showframe}

@@

            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize VF3}; &
            \node [anchor=center] {\includegraphics*{plots/graph-vf3-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{plots/graph-vf3-induced-nodes-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{plots/graph-vf3-induced-nodes-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{plots/graph-vf3-induced-nodes-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{plots/graph-vf3-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{plots/graph-vf3-induced-nodes-30-150.pdf}}; \\

@@

    of \cref{figure:non-induced}. The sixth row plots constrainedness using

@@

    location of the phase transition, and the dotted lines are $t_d=0.5$ and the $p_d=t_d$
    diagonal.}\label{figure:induced}
